%
% ---- Bibliography ----
%
\begin{thebibliography}{11}
%
\bibitem {berners}
Berners-Lee, Tim, James Hendler, and Ora Lassila. "The semantic web." Scientific american 284.5 (2001): 28-37.

\bibitem {miller}
Miller, Eric. "An introduction to the resource description framework." Bulletin of the American Society for Information Science and Technology 25.1 (1998): 15-19.

\bibitem {lehman}
Lehmann, Jens, et al. "DBpedia-a large-scale, multilingual knowledge base extracted from wikipedia." Semantic Web Journal 5 (2014): 1-29.

\bibitem {prud}
Prud, Eric, and Andy Seaborne. "Sparql query language for rdf." (2006).

\bibitem {mendes}
Mendes, Pablo N., et al. "DBpedia spotlight: shedding light on the web of documents." Proceedings of the 7th International Conference on Semantic Systems. ACM, 2011.

\bibitem {miller2}
Miller, George A. "WordNet: a lexical database for English." Communications of the ACM 38.11 (1995): 39-41.

\bibitem {jin}
Jin, Yohan, et al. "Image annotations by combining multiple evidence \& wordnet." Proceedings of the 13th annual ACM international conference on Multimedia. ACM, 2005.

\bibitem {shafer}
Shafer, Glenn. A mathematical theory of evidence. Vol. 1. Princeton: Princeton university press, 1976.

\bibitem {qian}
Qian, Xueming, and Xian-Sheng Hua. "Graph-cut based tag enrichment." Proceedings of the 34th international ACM SIGIR conference on Research and development in Information Retrieval. ACM, 2011.

\bibitem {cili}
Cilibrasi, Rudi L., and Paul Vitanyi. "The google similarity distance." Knowledge and Data Engineering, IEEE Transactions on 19.3 (2007): 370-383.

\bibitem {angel}
Angeletou, Sofia, et al. "Bridging the gap between folksonomies and the semantic web: An experience report." (2007).
\end{thebibliography}